Lattice model

### 2017-04-03 oopsla17/lattice-model.tex
Fix markup in inference

\begin{defn}{(Origin)}
In $N$-dimensions, the \emph{origin} $\mathbf{0}_N$ is the singleton set
$\{0^N\}$, or equivalently the vector of unit intervals $[0, 0]^N$.
\end{defn}

\begin{defn}{(Extended origin)}
In $N$-dimensions, the \emph{extended origin} is the
interval $[-1, 1]^N$ which is a subset of \region{N}.
\end{defn}

@@

This notion extends to sets of points. Since an
   there may be an infinite number of points, we measure the
  distance from the closest one.
\todo{Mistral to check: I may have broken this notion}
\end{defn}
%
\begin{prop}{}
  The closed form of extend origin distance for a set of $N$-dimensional
  points $P$ is written as $|P|$ and is defined:
%
  \begin{align*}
|P| & = \sum_{i=1}^{N} dist_i(P)
 &
    \textit{dist}_i(P) & = \begin{cases}
      0 & \pi_i(P) = \interv{-\infty}{\infty}{} \\
      \mathsf{a} - 1 & \pi_i(P) = \{\mathsf{a}\} \\
    \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
\todo{Not sure what we are going to prove here? That it is a metric
space or something?}
\end{proof}

\todo{We used to call the below property contiguity, and I think this is a natural
notion- does ``close neighbour'' have some standard use or is
it okay to call this contiguity?}
\begin{defn}{(Close neighbour)}
 A set of points $P$ is said to be a \emph{close neighbour at index $j$} of a set
   $P'$ if for every index $i$ except $j$, $\pi_i(P) = \pi_i(P')$
 but at $j$ then $\pi_j(P) \neq \pi_i(P')$ and
 $\textit{dist}_j(P) = \textit{dist}_i(P') + 1$.

\todo{Not sure how to rewrite the following as I have a bit of hard
time parsing it.}
  This necessarily means point vectors within the extended origin and the
  degenerate point offsets vector with \interv{-\infty}{\infty}{} does not have
  close neighbours.
\end{defn}
%
\begin{prop}
  The unique close neighbour at index $i$ of an $N$-dimensional set of
  points, if it exists, is given by the following partial function:
%
  \begin{align*}
    \mathit{close\_neighbour}(p,i) & = \prod^{N}_{j=1} \mathit{shift}(p,i,j) &
%
    \mathit{shift}(p,i,j) & =
      \begin{cases}
        \{a - 1\} & i = j \wedge \pi_i(p) = \{\mathsf{a}\} \wedge \mathsf{a} > 0\\
        \{a + 1\} & i = j \wedge \pi_i(p) = \{\mathsf{a}\} \wedge \mathsf{a} < 0\\
        \pi_j(p)  & otherwise
      \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
\todo{Hm- I guess uniqueness follows from this being a function rather
  than a relation? Seems fine no problem to prove- }
\end{proof}

>>>>

\begin{defn}{(Origin)}
  In $N$-dimensions, the \emph{origin} $\mathbf{0}_N$ is the singleton set
  $\{0^N\}$, or equivalently the vector of unit intervals $\interv{0}{0}{N}$.
\end{defn}

\begin{defn}{(Extended origin)}
  In $N$-dimensions, the \emph{extended origin} is the interval
  $\interv{-1}{1}{N}$ which is a subset of \region{N}.
\end{defn}

@@

  This notion extends to sets of points. Since an there may be an infinite
  number of points, we measure the distance from the closest one.

  \todo{Mistral to check: I may have broken this notion}
\end{defn}
%
\begin{prop}{}
  The closed form of extend origin distance for a set of $N$-dimensional
  points $P$ is written as $|P|$ and is defined:
%
  \begin{align*}
    |P| & = \sum_{i=1}^{N} dist_i(P)
    &
    \textit{dist}_i(P) & = \begin{cases}
      0 & \pi_i(P) = \interv{-\infty}{\infty}{} \\
      \mathsf{a} - 1 & \pi_i(P) = \{\mathsf{a}\} \\
    \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
  \todo{%
    Not sure what we are going to prove here? That it is a metric space or
    something?
  }
\end{proof}

\todo{%
  We used to call the below property contiguity, and I think this is a natural
  notion- does ``close neighbour'' have some standard use or is it okay to call
  this contiguity?
}
\begin{defn}{(Close neighbour)}
  A set of points $P$ is said to be a \emph{close neighbour at index $j$} of a
  set $P'$ if for every index $i$ except $j$, $\pi_i(P) = \pi_i(P')$ but at $j$
  then $\pi_j(P) \neq \pi_i(P')$ and $\textit{dist}_j(P) = \textit{dist}_i(P') +
  1$.

\todo{%
  Not sure how to rewrite the following as I have a bit of hard time parsing it.
}

  This necessarily means point vectors within the extended origin and the
  degenerate point offsets vector with \interv{-\infty}{\infty}{} does not have
  close neighbours.
\end{defn}
%
\begin{prop}
  The unique close neighbour at index $i$ of an $N$-dimensional set of
  points, if it exists, is given by the following partial function:
%
  \begin{align*}
    \mathit{close\_neighbour}(p,i) & = \prod^{N}_{j=1} \mathit{shift}(p,i,j) &
%
    \mathit{shift}(p,i,j) & =
      \begin{cases}
        \{a - 1\} & i = j \wedge \pi_i(p) = \{\mathsf{a}\} \wedge \mathsf{a} > 0\\
        \{a + 1\} & i = j \wedge \pi_i(p) = \{\mathsf{a}\} \wedge \mathsf{a} < 0\\
        \pi_j(p)  & otherwise
      \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
\todo{Hm- I guess uniqueness follows from this being a function rather
  than a relation? Seems fine no problem to prove- }
\end{proof}
